\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-17 foci/paper.tex
added email addresses

\title{\Large \bf Security Audit of Safeplug ``Tor in a Box''}
\author{
 {\rm Anne Edmundson}\\
 Princeton University
 \and
 {\rm Anna Kornfeld Simpson}\\
 Princeton University
 \and
 {\rm Joshua A. Kroll}\\
 Princeton University
 \and
 {\rm Edward W. Felten}\\
 Princeton University
} % end author

@@

\subsection{Information Prior to Using the Device: Terms of Service}
\label{tos}
The Terms of Service (TOS) are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.

One of the topics the TOS discusses is the use of open source software.  A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.  The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.  There is an open source page at \url{http://pogoplug.com/opensource}, which describes several pieces of software used by the Safeplug; however, there is no way to find this page from the Terms of Service or the Safeplug website.

@@

Figure~\ref{fig:boxandwhisker} displays the variation among fetch requests for each setting when fetching \url{www.coca-cola.com}.  The greater variation for settings using Tor leads us to believe that more than one Tor circuit was used.  Despite performing these fetches close in time, this variation shows that more than one Tor circuit was used, and therefore, we were not simply measuring the variation in Tor circuit performance.

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle (TBB), which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  A differentiating factor between the Safeplug and the TBB is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy against the other features of the TBB.  We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the TBB; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.  Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.  First, we recorded how many third party domains were accessed total (throughout the crawl); in addition, we recorded the total number of JavaScript and Flash objects received from third parties, as well as the total number of third party cookies received.  We then found the on-average, per-page numbers corresponding to these measurements by dividing the totals by 100.  These fractions are shown in Table~\ref{tbb}.

@@

\subsection{Spoofing the Installation Server}
\label{dnsspoof}
An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the initial installation process.  We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.  This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Because the activation occurs over TCP, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.  Note: We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process DOES occur over HTTPS.

>>>>

\title{\Large \bf Security Audit of Safeplug ``Tor in a Box''}
\author{
 {\rm Anne Edmundson}\\
 Princeton University\\
 annee@cs.princeton.edu
 \and
 {\rm Anna Kornfeld Simpson}\\
 Princeton University\\
 aksimpso@cs.princeton.edu
 \and
 {\rm Joshua A. Kroll}\\
 Princeton University\\
 kroll@cs.princeton.edu
 \and
 {\rm Edward W. Felten}\\
 Princeton University\\
 felten@cs.princeton.edu
} % end author

@@

\subsection{Information Prior to Using the Device: Terms of Service}
\label{tos}
The Terms of Service (TOS) are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website~\cite{safeplug}.

One of the topics the TOS discusses is the use of open source software.  A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.  The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html}, but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.  There is an open source page at \url{http://pogoplug.com/opensource}, which describes several pieces of software used by the Safeplug; however, there is no way to find this page from the Terms of Service or the Safeplug website.

@@

Figure~\ref{fig:boxandwhisker} displays the variation among fetch requests for each setting when fetching \url{www.coca-cola.com}.  Despite performing these fetches close in time, the greater variation for settings using Tor shows that more than one Tor circuit was used, and therefore, we were not simply measuring the variation in Tor circuit performance.

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle (TBB), which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  A differentiating factor between the Safeplug and the TBB is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the TBB, we must measure the value of Privoxy against the other features of the TBB.  We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the TBB; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.  Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.  First, we recorded how many third party domains were accessed total (throughout the crawl); in addition, we recorded the total number of JavaScript and Flash objects received from third parties, as well as the total number of third party cookies received.  We then found the on-average, per-page numbers corresponding to these measurements by dividing the totals by 100.  These fractions are shown in Table~\ref{tbb}.

@@

\subsection{Spoofing the Installation Server}
\label{dnsspoof}
An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the initial installation process.  We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.  This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Because the activation occurs over TCP, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.  We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS.
